---
title: "shinyconverter"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{shinyconverter}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# Introduction
shinyconverter is an R package that provides functions to convert distances, weights, and temperatures between different units. It also includes a Shiny app that demonstrates how to use these functions in a web-based interface.

In this vignette, we will walk through examples of using the shinyconverter package's functions and running the Shiny app.
```{r setup}
library(shinyconverter)
```
# Convert distances
To convert distances between different units, use the convert_distance function. For example, to convert 1 kilometer to miles:
```{r}
# Convert 1 kilometer to miles
convert_distance(1, "km", "mi")

```
# Convert weights
To convert weights between different units, use the convert_weight function. For example, to convert 1 kilogram to pounds:
```{r}
# Convert 1 kilogram to pounds
convert_weight(1, "kg", "lb")
```
# Convert temperatures
To convert temperatures between different units, use the convert_temperature function. For example, to convert 0 degrees Celsius to degrees Fahrenheit:
```{r}
# Convert 0 degrees Celsius to degrees Fahrenheit
convert_temperature(0, "C", "F")

```
# Running the Shiny app
shinyconverter includes a Shiny app that demonstrates how to use these functions in a web-based interface. To run the Shiny app, use the following code:
```{r}
shiny::runApp(system.file("shinyapp", package = "shinyconverter"))
```
